Ms 1

### 2017-06-19 ms1/ms1_display.Rmd
ms1 models, display

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)
import::from(forcats, as_factor)

@@

@@

Only in the cohort:

```{r}
read_tsv('tables/tbl_cohort_model_abx.tsv') %>%
  filter(term=='year', model %in% top_abx) %>%
  arrange(estimate) %>%
  mutate(cpkp_per_year=estimate*1000,
         antibiotic=as_factor(model)) %>%
  select(antibiotic, cpkp_per_year) %>%
  ggplot(aes(x=antibiotic, y=cpkp_per_year)) +
  geom_point() +
  coord_flip() +
  ggtitle('Adjusted changes in consumption') +
  theme_minimal()
```

@@

```{r}
read_tsv('tables/tbl_cohort_model_azithro.tsv') %>%
  mutate(cpkp=estimate*1000) %>%
  filter(term != '(Intercept)') %>%
  select(term, cpkp, p.value) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_model_levo.tsv') %>%
  mutate(cpkp=estimate*1000) %>%
  filter(term != '(Intercept)') %>%
  select(term, cpkp, p.value) %>%
  kable
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)
import::from(forcats, as_factor)
import::from(tools, md5sum)

@@

# Abstract

```{r}
model_ci = function(df) {
  mutate(df, ci_range=1.96*std.error,
         ci_low=estimate-ci_range,
         ci_high=estimate+ci_range)
}

model_ci_cpkp = function(df) {
  model_ci(df) %>%
    mutate_at(vars(ci_range, ci_low, ci_high, estimate), function(x) x * 1000) %>%
    rename(cpkp=estimate)
}

read_tsv('tables/tbl_cohort_model2.tsv') %>%
  filter(term=='year') %>%
  model_ci_cpkp() %>%
  kable

read_tsv('tables/tbl_cohort_model_abx.tsv') %>%
  filter(model %in% c('azithromycin', 'levofloxacin'), term=='year') %>%
  select(term, estimate, std.error, model) %>%
  model_ci_cpkp() %>%
  kable
```

@@

```{r adjusted_changes, cache.extra=md5sum('tables/tbl_cohort_model_abx.tsv')}
x = read_tsv('tables/tbl_cohort_model_abx.tsv') %>%
  filter(term=='year', model %in% top_abx) %>%
  arrange(estimate) %>%
  mutate(cpkp_per_year=estimate*1000,
         antibiotic=as_factor(model)) %>%
  select(antibiotic, cpkp_per_year)

p = x %>%
  ggplot(aes(x=antibiotic, y=cpkp_per_year)) +
  geom_point() +
  geom_linerange(aes(x=antibiotic, ymin=0, ymax=cpkp_per_year)) +
  coord_flip() +
  ggtitle('Adjusted changes in consumption') +
  xlab('') +
  ylab('adjusted yearly change in claims per 1,000 beneficiaries per year') +
  scale_y_continuous(limits=c(-16, 17), breaks=c(-15, -10, -5, 0, 5, 10, 15)) +
  theme_minimal()

show(p)
ggsave('fig/fig_adjusted_changes.pdf', plot=p)

x %>% kable
```

@@

```{r, cache.extra=md5sum('tables/tbl_cohort_model_azithro.tsv')}
read_tsv('tables/tbl_cohort_model_azithro.tsv') %>%
  model_ci_cpkp() %>%
  filter(term != '(Intercept)') %>%
  select(term, cpkp, ci_low, ci_high, p.value) %>%
  mutate_at(vars(cpkp, ci_low, ci_high), function(x) round(x, 1)) %>%
  kable
```

@@

```{r, cache.extra=md5sum('tables/tbl_cohort_model_levo.tsv')}
read_tsv('tables/tbl_cohort_model_levo.tsv') %>%
  model_ci_cpkp() %>%
  filter(term != '(Intercept)') %>%
  select(term, cpkp, ci_low, ci_high, p.value) %>%
  mutate_at(vars(cpkp, ci_low, ci_high), function(x) round(x, 1)) %>%
  kable
```
